A large-scale analysis of racial disparities in police stops across the United

### 2020-03-04 lib/paper_results.Rmd
removing pfs summary table from output repot
Add aesthetic tweaks

```{r search_rates_summary}
pfs$summary_table %>% 
  mutate(agency = if_else(City == "--", "state", "city")) %>% 
  group_by(agency) %>% 
  mutate(ct = 1:n()) %>% 
  ungroup() %>% 
  select(-agency) %>% 
  select(ct, everything()) %>% 
  kable("latex")
```

@@

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
disp$state$outcome$plots$aggregate + theme(legend.position = "none")
```

@@

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) - 0.05, 0
)
axis_max <- min(
  max(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) + 0.05, 1
)
disp$city$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + theme(legend.position = "none")
```

@@

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$search_rate
```

@@

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$hit_rate
```

@@

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$search_rate
```

@@

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$hit_rate
```

@@

```{r mj_inferred_threshold_plot, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_1$plot
```

>>>>

@@

```{r disparity-state-hit_rates-plot, fig.height=6, fig.width=10}
axis_min <- max(
  min(
    disp$state$outcome$plots$aggregate$data$minority_rate,
    disp$state$outcome$plots$aggregate$data$majority_rate
  ) - 0.03, 0
)
axis_max <- min(
  max(
    disp$state$outcome$plots$aggregate$data$minority_rate,
    disp$state$outcome$plots$aggregate$data$majority_rate
  ) + 0.03, 1
)

disp$state$outcome$plots$aggregate + 
  theme(
    legend.position = "none",
    plot.title = element_blank()
  ) +
  scale_x_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-city-thresholds-plot, fig.height=5, fig.width=10}
axis_min <- max(
  min(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) - 0.03, 0
)
axis_max <- min(
  max(
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$minority_rate,
    disp$city$threshold$prior_scaling_factor_1$plots$aggregate$data$majority_rate
  ) + 0.03, 1
)
disp$city$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank()) + 
  scale_x_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1), expand = c(0,0)
  ) + 
  scale_y_continuous(
    limits = c(axis_min, axis_max), breaks = seq(0, .5, 0.05),
    labels = scales::percent_format(accuracy = 1),expand = c(0,0)
  ) 
```

@@

```{r disparity-state-thresholds-plot, fig.height=5, fig.width=10}
disp$state$threshold$prior_scaling_factor_1$plots$aggregate + 
  theme(legend.position = "none", plot.title = element_blank())
```

@@

```{r disparity-city-ppc-search, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$search_rate + 
  scale_y_continuous(
    "Search rate prediction error\n",
    limits = c(-.016, .016), breaks = seq(-.5, .5, 0.005),
    labels = scales::percent_format(accuracy = 0.1)
) +
    scale_x_continuous(
        "\nPredicted search rate",
        limits = c(0, .27), breaks = seq(0, .5, 0.05),
        labels = scales::percent_format(accuracy = 1), expand = c(0,0)
    ) +
  theme(plot.title = element_blank())
```

@@

```{r disparity-city-ppc-hit, fig.height=5, fig.width=8}
disp$city$threshold$prior_scaling_factor_1$ppc$hit_rate +
    scale_y_continuous(
        "Hit rate prediction error\n",
        limits = c(-.21, .21), breaks = seq(-.5, .5, 0.05),
        labels = scales::percent_format(accuracy = 1)
    ) +
    scale_x_continuous(
        "\nPredicted hit rate",
        limits = c(0, .37), breaks = seq(0, .5, 0.05),
        labels = scales::percent_format(accuracy = 1), expand = c(0,0)
    ) +
    theme(plot.title = element_blank())
```

@@

```{r disparity-state-ppc-search, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$search_rate +
  scale_y_continuous(
        "Search rate prediction error\n",
        limits = c(-.021, .021), breaks = seq(-.5, .5, 0.005),
        labels = scales::percent_format(accuracy = .1)
    ) +
    scale_x_continuous(
        "\nPredicted search rate",
        limits = c(0, .11), breaks = seq(0, .5, 0.02),
        labels = scales::percent_format(accuracy = 1), expand = c(0,0)
    ) +
  theme(plot.title = element_blank())
```

@@

```{r disparity-state-ppc-hit, fig.height=5, fig.width=8}
disp$state$threshold$prior_scaling_factor_1$ppc$hit_rate + 
  scale_y_continuous(
        "Hit rate prediction error\n",
        limits = c(-.30, .30), breaks = seq(-.5, .5, 0.05),
        labels = scales::percent_format(accuracy = 1)
    ) +
    scale_x_continuous(
        "\nPredicted hit rate",
        limits = c(0, .65), breaks = seq(0, .8, 0.1),
        labels = scales::percent_format(accuracy = 1), expand = c(0,0)
    ) +
  theme(plot.title = element_blank())
```

@@

```{r mj_inferred_threshold_plot, fig.height=5, fig.width=10}
mj$plots$inferred_threshold_changes$prior_scaling_factor_1$plot +
  theme_bw(base_size = 20) +
  theme(
    panel.grid = element_blank(),
    legend.background=element_rect(fill="transparent"),
    legend.position=c(0.65, 0.25)
  )
```
